What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-19 lda-paper.tex
- [X] Address this comment: You say that you remove stop words, but in Figure 4 I noticed words like "to" or "on". These are stop words.
- [X] Specify that if in 1 CASE we removed these words we got different results: You state that words like "diffs, annotate, history" should be treated as stop words. Why? Is it because they do not denote a domain concept? What if the domain actually include these words, are they still not relevant?  Dealt with in the case study

We found there were common words across topic clusters, such as
\emph{diffs}, \emph{annotate} and \emph{history}; since these words
occur so often in the MySQL 3.23 messages, we probably should be
viewed as stop words. There were notable transitional topics such as
in the first window the word \emph{BitKeeper} appears because MySQL
adopted Bitkeeper for their source control system yet in the following
windows there were no mentions of BitKeeper. \emph{RENAME} also only
appeared once in the first window and never again. Per each topic we
tried to identify the purpose of the topic; to our surprise we found
that even with only a little familiarity with the code base that
naming the topic was straightforward. To find the purpose of a commit
we looked at the most frequent words in the word distribution of the
topic and tried to summarize the topic, then we looked into the
commits related to that topic to investigate if we were correct; since
the commit messages and the word distribution share the same words the
purpose extracted from commit comments was usually accurate.

@@

\begin{figure*}
  \centering
%  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \includegraphics[width=1.0\textwidth]{time-smear-plot}%fixed-time-smear-plot-scaled}
  \caption{Compact-trend-view shows topics per month for MaxDB
    7.500. The x-axis is time in months, the Y axis is used to stack
    topics occurring at the same time. Trends that are continuous are
    plotted as continuous blocks. The top 10 words in the topics are
    joined and embedded in box representing the topics. The gap in the
    middle is a period where no development took place.}
  \label{fig:topicsmear}
\end{figure*}

>>>>

We found there were common words across topic clusters, such as
\emph{diffs}, \emph{annotate} and \emph{history}; since these words
occur so often in the MySQL 3.23 messages. These words probably should
be viewed as stop words since occur across so many topics, even though
they are related to version control usage.  There were notable
transitional topics such as in the first window the word
\emph{BitKeeper} appears because MySQL adopted Bitkeeper for their
source control system yet in the following windows there were no
mentions of BitKeeper. \emph{RENAME} also only appeared once in the
first window and never again. Per each topic we tried to identify the
purpose of the topic; to our surprise we found that even with only a
little familiarity with the code base that naming the topic was
straightforward. To find the purpose of a commit we looked at the most
frequent words in the word distribution of the topic and tried to
summarize the topic, then we looked into the commits related to that
topic to investigate if we were correct; since the commit messages and
the word distribution share the same words the purpose extracted from
commit comments was usually accurate.

@@

\begin{figure*}
  \centering
%  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \includegraphics[width=1.0\textwidth]{time-smear-plot}%fixed-time-smear-plot-scaled}
  \caption{Compact-trend-view shows topics per month for MaxDB
    7.500. The x-axis is time in months, the Y axis is used to stack
    topics occurring at the same time. Trends that are continuous are
    plotted as continuous blocks. The top 10 words in the topics are
    joined and embedded in box representing the topics. No stop words were removed. The gap in the
    middle is a period where no development took place.}
  \label{fig:topicsmear}
\end{figure*}
